Prediction is Hard (Especially About the Future)

### 2015-08-08 Manuscript.tex
Updates from @rahlk's local machine.

\maketitle
\begin{abstract}
This paper provides ...  
\end{abstract}
\section{Introduction}
\section{Cluster and Contrast}
A recurring data analysis pattern in this paper is $cluster+contrast$. The data is distilled into a few clusters using a clustering scheme. Then lessons are inferred by studying the differences between these clusters. These lessons are used to generate rules that can be applied in any context.
\subsection{Clustering}
There are a wide variety of clustering methods to choose from. A study by Ganesan~\cite{div14} explored different clustering methods for software engineering data using the effort and defect data from the PROMISE repository~\cite{promise}. In that study methods such as WHERE, K-Means, mini-batch-K-Means, DBScan, EM, and Ward were investigated. The results of the study showed that the size and number of clusters is more important that the specifics of the techniques used.

@@

Clustering is followed generating \textit{contrast sets}. These contrast sets represent recommendations on what could be altered to better improve an outcome. In this work we have explored several algorithms as possible tools to identify contrast between clusters. These fall into two broad categories:
\begin{enumerate}
\item Case Based Reasoning techniques (Nearest Neighbors and a gradient base planner called HOW)
\item Decision Trees.
\end{enumerate}

@@

\subsubsection{Case Based Reasoning}

@@

Simple though this method may seem, using nearest neighbors presents a couple of significant challenges: 
\begin{itemize}
\item[1.] Displacements are seldom limited to small regions, this implies that large changes may be recommended when not necessary. This may make the solutions less feasible to implement. 
\item[2.] The nearness of a test case to a cluster in the training data is subjective. This affects the locality of the solutions, thus jeopardizing the relevance of these changes to the test case under consideration.
\end{itemize}

@@

\subsubsection{HOW}

HOW is very different compared to conventional CBR planners in that it explores the gradient between pairs of nearby clusters instead of studying the clusters themselves. HOW works by clustering the data during training using WHERE and then drawing \texttt{slopes} between the centroids of pairs of nearby clusters. Assuming the cluster pairs are labeled X and Y, with X having slightly better performance score than Y, the \texttt{slope} between X and Y acts as an indicator pointing to a direction to displace the data; i.e. away from Y and towards X.

@@

Although HOW manages to generate plans by localizing displacements to regions small enough to produce a statistically significant improvement, it needs to be noted that it fails to provide succinct summaries. Lack of succinctness makes it difficult draw generalizable conclusions about the test data.

This is a trend commonly observed in most CBR systems. They tend to reason directly from a loaded training data instead of first summarizing the data into a model. However, not all domains come with reliable models. For instance, a model that encompasses all the intricate issues that may lead to defects in software would be very large and indeed rather complex. In addition to this, finding empirical data to validate such models can be hard to come by and also time consuming ~\cite{me09i,me09j}. Fortunately, this issue can be circumvented by using decision trees.

%\begin{figure}[t!]
%	\small
%	~\hrule~
%	
%	{\bf \fig{where}a: top down clustering:}
%	
%		The data is recursively divided in clusters using WHERE as follows:
%		\begin{itemize}
%			
%			\item Find   two   distance cases,  $X,Y$
%			by picking any case $W$ at random, then setting $X$ to its most
%			distant case, then setting $Y$ to the case most distant from
%			$X$
%			(this requires only $O(2N)$ comparisons
%			of $N$ cases).
%			\item Project each case $Z$
%			onto a {\tt Slope} that  runs between $X,Y$ using the cosine
%			rule. 
%			\item Split the data at the median $X$ value of all cases and
%			recurses on each half  (stopping when
%			one half has less  than $\sqrt{N}$ of the original population).
%		\end{itemize}
%	
%	~\hrule~
%	
%	{\bf \fig{where}b: finding distances:}
%	
%	In the \fig{where}a, to compute distances, we use
%	the Euclidean measure recommended for
%	case-based reasoning by Aha et al.~\cite{aha91};
%	i.e. $\sqrt{\sum_iw_i(X_i-Y_i)^2}$ where $X_i,Y_i$
%	where values are  normalized 0..1 for the range min..max and 
%	$w_i$ is some importance weight given to attribute $i$.
%	Usually, $w_i=1$ but it can be adjusted using, say,
%	the feature weighting methods of \fig{where}d. 
%	
%	~\hrule~
%	
%	{\bf \fig{where}c: 3 point geometry:}
%	
%	Let   $X,Y$ be two points joined by  a {\em Slope} of  length $c$.
%	A third point, $Z$, has distances  $a=dist(Z,X)$ and
%	$b=dist(Z,Y)$ to $X,Y$, respectively.
%	According to the cosine rule,   $Z$ projects onto  $\overline{XY}$
%	at distance $x=(a^2 + c^2 - b^2)/(2c)$ from $X$.
%	Further, according to Pythagoras' theorem, $Z$ stands at a distance
%	$y = \sqrt{a^2 - x^2}$ from the line $\overline{XY}$. 
%	
%	~\hrule~
%	
%	{\bf \fig{where}d: feature weighting:}
%	
%	HERE's feature weighting algorithm
%	comes from the CART regression tree learner~\cite{Breiman1984}.
%	It sorts independent variables
%	according to how well they can reduce the variability
%	of a  numeric objective.
%	If we split some column $i$ of independent numeric data  into $N=n_1 + n_2 + ..$ splits,
%	then the expected
%	value of the objective value of the split  is $w_i = \sum_i v_in_i/N$
%	where $v$ is the standard deviation of the objective.
%	A recursive procedure can  find those divisions $n_1,n_2,...$ by (a)~sorting a numeric column,
%	then split at $\argmin_i w_i$, then recursing into each half.
%	
%	~\hrule~
%	
%	\caption{Sub-routines within HOW.}\label{fig:where}
%\end{figure}

\subsubsection{Decision Trees}

\section{CROSSTREES}
\subsection{Design}
	\begin{figure}[t]
		\small
		~\hrule~

@@

\subsection{Assessment}
\section{Experiments}
\subsection{Data}

\begin{figure*}[!t]
\scriptsize
   \begin{center}
   \begin{minipage}{.46\linewidth}
    \begin{tabular}{r@{~}|l@{~}|r@{~}|l@{~}|r@{~}|r@{~}|} \cline{2-6}
   & \multicolumn{5}{c|}{ }\\

@@

    \caption{Training and test {\em data set properties} for the Jureczko data sets,
    sorted in ascending order of \% defective examples.
    On the right-hand-side, we show the {\em results from learning}.
    Data is ``good'' if it has recall over 60\% and false alarm under 40\%
(and note that, after tuning, there are more ``good'' than before).
Data   marked with ``$\star$'' show large improvements in performance, after tuning.
Data   marked with ``$\times$'' are ``not good'' since their test suites  have so few non-defective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
}\label{fig:j}
\end{figure*}
\subsection{When not to Plan?}
\subsection{Evaluation}
\subsection{Results}
\section{Threats to Validity}
\section{Conclusion}
\section*{Acknowledgements}
\bibliographystyle{plain}

>>>>

\maketitle
\begin{abstract}
This paper provides ...  
\end{abstract}
\section{Introduction}

\section{Cluster and Contrast}

A recurring data analysis pattern in this paper is $cluster+contrast$. The data is distilled into a few clusters using a clustering scheme. Then lessons are inferred by studying the differences between these clusters. These lessons are used to generate rules that can be applied in any context.

\subsection{Clustering}
There are a wide variety of clustering methods to choose from. A study by Ganesan~\cite{div14} explored different clustering methods for software engineering data using the effort and defect data from the PROMISE repository~\cite{promise}. In that study methods such as WHERE, K-Means, mini-batch-K-Means, DBScan, EM, and Ward were investigated. The results of the study showed that the size and number of clusters is more important that the specifics of the techniques used.

@@

Clustering is followed by generating \textit{contrast sets}. These contrast sets represent recommendations on what could be altered to better improve an outcome. In this work we have explored several algorithms as possible tools to identify contrast between clusters. These fall into two broad categories:
\begin{enumerate}
\item Case Based Reasoning techniques (Nearest Neighbors and a gradient base planner called HOW)
\item Decision Trees.
\end{enumerate}

@@

\subsection{Case Based Reasoning}

@@

Simple though this method may seem, using nearest neighbors presents a couple of significant challenges: 
\begin{itemize}
\item[1.] Displacements are seldom limited to small regions, this implies that large changes may be recommended when they are not necessary. This may make the solutions less feasible to implement. 
\item[2.] The nearness of a test case to a cluster in the training data is subjective. This affects the locality of the solutions, thus jeopardizing the relevance of these changes to the test case under consideration.
\end{itemize}

@@

\subsection{HOW}

HOW is very different compared to conventional CBR planners in that it explores the gradient between pairs of nearby clusters instead of studying the clusters themselves. HOW works by clustering the data during training using WHERE and then drawing \texttt{slopes} between the centroids of pairs of nearby clusters. Assuming the cluster pairs are labeled X and Y, with X having slightly better performance score than Y, the \texttt{slope} between X and Y acts as an indicator pointing to a direction in which to displace the data; i.e. away from Y and towards X.

@@

Although HOW manages to generate plans by localizing displacements to regions small enough to produce a statistically significant improvement, it needs to be noted that it fails to provide succinct summaries. Lack of succinctness makes it difficult draw generalizable conclusions about the test data. This is a trend commonly observed in most CBR systems. They tend to reason directly from a loaded training data instead of first summarizing the data into a model.

% However, not all domains come with reliable models. For instance, a model that encompasses all the intricate issues that may lead to defects in software would be very large and indeed rather complex. In addition to this, finding empirical data to validate such models can be hard to come by and also time consuming ~\cite{me09i,me09j}.

\begin{figure}[t]
	\small
	~\hrule~

@@

\subsection{CROSSTREES}

Like all the previous planners, CROSSTREES starts by clustering the training data. Following this, it executes a decision tree algorithm using the clusters as class labels. Using a decision tree algorithm allows us to identify the most informative attributes to select in different clusters. The decision tree built in this fashion emulates a model built from the training data.

Using the decision tree, the test cases can be categorized into one of the branches of the tree. Now, to generate the contrast sets, we determine (1) What \textit{current} branch does a test case fall in?; (2) What \textit{desired} branch would the test case have to move to?; (3) What are the deltas between \textit{current} and \textit{desired}? The last question can be answered by finding the deltas in branches of the decision tree that lead to \textit{desired} from \textit{current}. For full algorithmic details, refer to \fig{xtrees_bare}.

CROSSTREES offer a great number of benefits compared to the other methods that were discussed above. Firstly, they offer a visual medium for experts to identify and explore solutions spaces that are local to the problem. Secondly, they offer solutions that are much more stable than other instance based learners. This stability can be attributed to the consistency and general reproducibility of the tree structure. Thirdly, and perhaps most importantly, the tree summarizes the training data succinctly, making it easier for a business user to examine the solutions.

A tree structure such as CROSSTREES are characterized by attributes such as size and depth. It is worth noting that these attributes have a profound impact on its performance. Our initial motivation for using CROSSTREES is that they can serve as a medium for experts to reason about a data. The size of the tree, if too large, jeopardizes the readability of the solutions by increasing the complexity. We have, therefore, endeavored to reduce the size of the tree by pruning away irrelevant solutions that do not contribute to better solutions (refer to step-2 of \fig{xtrees_bare})

\section{Experiments}

\subsection{Data}

\begin{figure*}[htbp!]
	\renewcommand{\baselinestretch}{0.8}\begin{center}
		{\scriptsize
			\begin{tabular}{c|l|p{4.7in}}
				amc & average method complexity & e.g. number of JAVA byte codes\\\hline
				avg\, cc & average McCabe & average McCabe's cyclomatic complexity seen
				in class\\\hline
				ca & afferent couplings & how many other classes use the specific
				class. \\\hline
				class. \\\hline
				cam & cohesion amongst classes & summation of number of different
				types of method parameters in every method divided by a multiplication
				of number of different method parameter types in whole class and
				number of methods. \\\hline
				cbm &coupling between methods &  total number of new/redefined methods
				to which all the inherited methods are coupled\\\hline
				cbo & coupling between objects & increased when the methods of one
				class access services of another.\\\hline
				ce & efferent couplings & how many other classes is used by the
				specific class. \\\hline
				dam & data access & ratio of the number of private (protected)
				attributes to the total number of attributes\\\hline
				dit & depth of inheritance tree &\\\hline
				ic & inheritance coupling &  number of parent classes to which a given
				class is coupled (includes counts of methods and variables inherited)
				\\\hline
				lcom & lack of cohesion in methods &number of pairs of methods that do
				not share a reference to an case variable.\\\hline
				locm3 & another lack of cohesion measure & if $m,a$ are  the number of
				$methods,attributes$
				in a class number and $\mu(a)$  is the number of methods accessing an
				attribute, 
				then
				$lcom3=((\frac{1}{a} \sum, j^a \mu(a, j)) - m)/ (1-m)$.
				\\\hline
				loc & lines of code &\\\hline
				max\, cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
				in class\\\hline
				mfa & functional abstraction & number of methods inherited by a class
				plus number of methods accessible by member methods of the
				class\\\hline
				moa &  aggregation &  count of the number of data declarations (class
				fields) whose types are user defined classes\\\hline
				noc &  number of children &\\\hline
				npm & number of public methods & \\\hline
				rfc & response for a class &number of  methods invoked in response to
				a message to the object.\\\hline
				wmc & weighted methods per class &\\\hline
				\rowcolor{lightgray}
				defect & defect & Boolean: where defects found in post-release bug-tracking systems.
			\end{tabular}
		}
	\end{center}
	\caption{OO measures used in our defect data sets.  Last line is
		the dependent attribute (whether a defect is reported to  a
		post-release bug-tracking system).}\label{fig:ck}
\end{figure*}

\subsection{When not to Plan?}
\begin{figure*}[!t]
	\scriptsize
	\begin{center}
		\begin{minipage}{.46\linewidth}
			\begin{tabular}{r@{~}|l@{~}|r@{~}|l@{~}|r@{~}|r@{~}|} \cline{2-6}
				& \multicolumn{5}{c|}{ }\\

@@

	\caption{Training and test {\em data set properties} for the Jureczko data sets,
		sorted in ascending order of \% defective examples.
		On the right-hand-side, we show the {\em results from learning}.
		Data is ``good'' if it has recall over 60\% and false alarm under 40\%
		(and note that, after tuning, there are more ``good'' than before).
		Data   marked with ``$\star$'' show large improvements in performance, after tuning.
		Data   marked with ``$\times$'' are ``not good'' since their test suites  have so few non-defective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
	}\label{fig:j}
\end{figure*}

\subsection{Assessment}
\subsection{Results}
\section{Threats to Validity}
\section{Conclusion}
\section*{Acknowledgements}
\bibliographystyle{plain}
